\section{Bibliografia}
\begin{thebibliography}{H}
    \bibitem{impacts-games-behaviours}
    Muhannad Quwaider, Abdullah Alabed and Rehab Duwairi. (2019). The Impact of Video Games on the Players Behaviors: A Survey. \textit{Procedia Computer Science} vol. 151, 575-582

	\bibitem{ethics-single}
	Erica Neely. (2016). \textit{The Ethics of Choice in Single-Player Video Games}. 
	
	\bibitem{only-game}
	Michael Heron, Pauline Belford. (2014). 'It's only a game' - ethics, empathy and identification in game morality systems. \textit{The Computer Games Journal} 3, 34-54
	
	\bibitem{free-will}
	Christopher Bartel. (2015). Free will and moral responsability in video games. \textit{Ethics and Information Technology} 17, 285-293
	
	\bibitem{papers}
	Paul Formosa, Malcolm Ryan and Dan Staines. (2016). Papers, Please and the systemic approach to engaging ethical expertise in videogames. \textit{Ethics and Information Technology} 18, 211-225
	
	\bibitem{mass-media}
	Jennifer E van Bekkum, and Shona Hilton. (2013). Primary care nurses' experiences on how the mass media influence frontline healthcare in the UK. \textit{BMC Family Practice} 14, 178
	
	\bibitem{suicide-risk}
	Yoshiki Koga and Daisuke Kawashima. (2019). The Relationship Between Video Game Play and Suicide Risk Among Japanese Young Adults.
	
	\bibitem{new-york-times}
	Laura Parker. (2019). Depressed and Anxious? These Video Games Want to Help. \textit{The New York Times}. Retrieved from \url{https://www.nytimes.com/2019/03/24/technology/personaltech/depression-anxiety-video-games.html}
	
	\bibitem{measure-morality}
	Malcolm Ryan, Paul Formosa, Stephanie Howarth, Dan Staines. (2020). Measuring morality in videogames research. \textit{Ethics and Information Technology} 22, 55-68.
	
	\bibitem{moral-foundation}
	The Moral Foundations Theory. \url{https://moralfoundations.org/}
	
	\bibitem{kremar-cingel}
	Marina Krcmar and Drew P. Cingel. (2016). Moral Foundations Theory and Moral Reasoning in Video Game Play: Using Real-Life Morality in a Game Context, \textit{Journal of Broadcasting \& Electronic Media} 60:1, 87-103
	
	\bibitem{joeckel}
	Sven Joeckel, Nicholas David Bowman and Leyla Dogruel. (2012). Gut or Game? The Influence of Moral Intuitions on Decisions in Video Games, \textit{Media Psychology} 15:4, 460-485
	
	\bibitem{weaver-lewis}
	Andrew J. Weaver and Nicky Lewis. (2012). Mirrored Morality: An Exploration of Moral Choice in Video Games, \textit{Cyberpsychology, Behavior, and Social Networking} Nov 2012, 610-614
	
	\bibitem{grizzard}
	Matthew Grizzard, Ron Tamborini, Robert J. Lewis, Lu Wang, and Sujay Prabhu. (2014). Being Bad in a Video Game Can Make Us Morally Sensitive, \textit{Cyberpsychology, Behavior, and Social Networking} Aug 2014, 499-504
	
\end{thebibliography}